Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
fix previous merge conflict

\section{Inductive Lemmata}
\label{sec:induction}
First we present several lemmata which play a crucial role in the inductive step of the proof of the main theorem, Theorem ~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$. While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-order} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-order} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}

@@

In Lemma \ref{lem:sat-1} we provide an inductive method to strengthen
O'Dorney's result \todo{cite theorem 8, Aaron: If you want to cite Theorem 8, just do \cite[Theorem 8]{dorney:canonical}} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
degrees at most $e = \max(\beta_i)$ with relations generated in
degrees at most $2e$. \todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective? If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
divisors. \todo{cite theorem 8.3.1} \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}

@@

@@

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
\end{longtable}
\todo{Possibly add an autoincrement counter to deal with table numbering}

>>>>

\section{Inductive Lemmata}
\label{sec:induction}
First we present several lemmata which play a crucial role in the
inductive step of the proof of the main theorem, Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove
Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which describe the generators and relations of $R_{D + \frac{\alpha
}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in
Subsection ~\ref{ssec:raise-orders}, we prove Lemma
~\ref{lem:raise-stacky-order}, which the generators and relations 
of the log spin canonical ring curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a 
curve with a certain subset of the $e_ i'$ incremented by $2$. 
While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
half-canonical divisors, although even Lemma
~\ref{lem:raise-stacky-order} has certain generalizations, as noted
in Remark ~\ref{rem:raise-fractional-order}

@@

In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
degrees at most $e = \max(\beta_i)$ with relations generated in
degrees at most $2e$. \todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective? If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
Zureick-Brown \cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
divisors. \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}

@@

\todo{label/ref of long tables doesn't work!}

@@

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
\end{longtable}
\todo{Possibly add an autoincrement counter to deal with table numbering}
\todo{label/ref of long tables doesn't work!}
